(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-27 ms.tex
EPIC 201912552 section. I now have this EPIC memorized. Time for PuppyButtonFace.

\newcommand{\rprs}{{$R_p/R_{\star}$}}

@@

\section{Potentially Interesting Systems}
\subsection{The One Around the M dwarf}

\subsection{Some Multi (possible multi of these}

>>>>

\newcommand{\rprs}{{$R_p/R_{\star}$}}
\newcommand{\ars}{{$a/R_{\star}$}}

@@

\section{Potentially Interesting Systems}
\subsection{A Mini-Neptune with Earthlike Insolation}

Of particular interest is EPIC 201912552.

By combining archival and modern seeing-limited data with adaptive optics 
imaging, we can exclude the possibility these transit events are caused by 
a background eclipsing binary.
The apparent transits must be caused by an object co-moving with EPIC 201912552;
radial velocities eliminate the possibility the companion is nonplanetary.
Therefore, we confirm the planetary nature of this system.

This star is an M2.8 dwarf at a distance of \btmtodo{Distance: around 30 pc}.
Of our planet candidate hosts, only EPIC 201367065 \citep[originally
discovered by][]{Crossfield15} is brighter in $K$-band.
This star is only 0.1 magnitudes fainter in $K$ than GJ\,1214 
\citep{Charbonneau09}.
Due to the relative brightness of the host star, this target is likely
to become a prime target for atmospheric characterization studies
and is ideal as a target for future space-based missions such as JWST.

Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated. 
Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
K, meaning its bulk insolation is similar to that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14}, 
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by 
\kep.

\subsection{EPIC 201465501?}
Is this a subsection? It's a star with a mass of ~0.2 Msun and a cnadidate with
a period of 18 days. I suppose it depends on the FPP.

\subsection{An Instrumental False Positive}

EPIC 201555883 was originally listed in \paperit\ as a planet candidate.

\subsection{Multiple Planet Systems}
